---
title: Table
author: Masatoshi Katabuchi
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
#rmdformats::material
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: TRUE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
      toc: true
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
```

This R markdown file contains the code to reproduce the Table 1 in "Hydraulic prediction of drought-induced plant dieback and top-kill depends on leaf habit and growth form" by Chen Ya-Jun et al. in Ecology Letters.

# Packages

```{r, cache=FALSE}
#rm(list = ls())
set.seed(123)
library(tidyverse)
library(rstanarm)
library(tictoc)
library(kableExtra)
#rstan::rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores()) # Run on multiple cores

theme_set(theme_bw())
```

# Data

```{r}
d <- read_csv("data/traits.csv") %>%
  mutate(Leafhabit2 = ifelse(Leafhabit == "D", "D", "E_SD"))

d <- d %>%
  rename(log10KS = KS) %>%
  rename(log10LMA =  LMA) %>%
  rename(log10rleaf =  rleaf) %>%
  rename(log10SWCleaf =  SWCleaf) %>%
  rename(log10epsilon =  epsilon) %>%
  rename(log10Cft =  Cft) %>%
  rename(log10WOODSWC =  WOODSWC) %>%
  mutate(log10KS =  log10(log10KS)) %>%
  mutate(log10LMA =  log10(log10LMA)) %>%
  mutate(log10rleaf =  log10(log10rleaf)) %>%
  mutate(log10SWCleaf =  log10(log10SWCleaf)) %>%
  mutate(log10epsilon =  log10(log10epsilon)) %>%
  mutate(log10Cft =  log10(log10Cft)) %>%
  mutate(log10WOODSWC =  log10(log10WOODSWC))

tmp <- names(d)[5:23]

dl <- d %>%
  pivot_longer(tmp)
dl
```

# Model for traits

First, we model leaf and stem traits, hydraulic safety margins among three leaf habit types and three growth forms.

```{r, eval=TRUE}
n_iter <- 2000
n_chain <- 4
my_prior <- normal(location = 0, scale = 2.5, autoscale = TRUE)
my_prior_aux <- cauchy(location = 0, scale = 2.5, autoscale = TRUE)

tic()
nd_anova <- dl %>%
  group_by(name) %>%
  nest() %>%
  mutate(data2 = map(data, ~ filter(., !is.na(value)))) %>%
#  head(3) %>%
  mutate(trait_LH = map(data2, ~  stan_glmer(value ~ 0 +  (1|Leafhabit),
                                    iter = n_iter,
                                    chains = n_chain,
                                    refresh = 0,
                                    prior = my_prior,
                                    prior_aux = my_prior_aux,
                                    prior_intercept = my_prior,
                                    adapt_delta = 0.99,
                                    data = ., family = gaussian))) %>%
  mutate(trait_LF = map(data2, ~  stan_glmer(value ~ 0 +  (1|Lifeform),
                                    iter = n_iter,
                                    chains = n_chain,
                                    refresh = 0,
                                    prior = my_prior,
                                    prior_aux = my_prior_aux,
                                    prior_intercept = my_prior,
                                    adapt_delta = 0.99,
                                    data = ., family = gaussian)))
toc()

```


Here are utility functions to get posterior distributions.

```{r}
sig_fun <- function(fit) {
  p_mat <- as_tibble(fit) %>%
      rename(
            D = `b[(Intercept) Leafhabit:D]`,
            E = `b[(Intercept) Leafhabit:E]`,
            S = `b[(Intercept) Leafhabit:SD]`) %>%
      mutate(E_S = E -  S) %>%
      mutate(S_D = S -  D) %>%
      mutate(E_D = E -  D)
  lwr <- 1 - 0.05/6
  upr <- 0 + 0.05/6
  lwr2 <- p_mat %>%
    dplyr::select(6:8) %>%
    apply(., 2, function(x)quantile(x, lwr))
  upr2 <- p_mat %>%
    dplyr::select(6:8) %>%
    apply(., 2, function(x)quantile(x, upr))
  # +1 indicautes signficance
   sign(lwr2 * upr2)
}

sig_fun2 <- function(fit) {
fit <- nd_anova$trait_LF[[1]]
  p_mat <- as_tibble(fit) %>%
      rename(
            L = `b[(Intercept) Lifeform:L]`,
            S = `b[(Intercept) Lifeform:S]`,
            T = `b[(Intercept) Lifeform:T]`) %>%
      mutate(L_S = L -  S) %>%
      mutate(S_T = S -  T) %>%
      mutate(L_T = L -  T)
  lwr <- 1 - 0.05/6
  upr <- 0 + 0.05/6
  lwr2 <- p_mat %>%
    dplyr::select(6:8) %>%
    apply(., 2, function(x)quantile(x, lwr))
  upr2 <- p_mat %>%
    dplyr::select(6:8) %>%
    apply(., 2, function(x)quantile(x, upr))
  # +1 indicautes signficance
   sign(lwr2 * upr2)
}

mean_fun <- function(fit) {
#  fit <- nd_anova$trait_LH[[3]]
  p_mat <- as_tibble(fit) %>%
      rename(
            D = `b[(Intercept) Leafhabit:D]`,
            E = `b[(Intercept) Leafhabit:E]`,
            SD = `b[(Intercept) Leafhabit:SD]`)  %>%
  dplyr::select(E, SD, D)
  means <- p_mat %>%
    apply(., 2, mean)
  means %>% round(2)
}

mean_fun2 <- function(fit) {
  p_mat <- as_tibble(fit) %>%
      rename(
            L = `b[(Intercept) Lifeform:L]`,
            S = `b[(Intercept) Lifeform:S]`,
            T = `b[(Intercept) Lifeform:T]`) %>%
  dplyr::select(L, S, T)
  means <- p_mat %>%
    apply(., 2, mean)

  means %>% round(2)
}

letter_fun <- function(fit) {
#  fit <- nd_anova$trait_LH[[3]]
  p_mat <- as_tibble(fit) %>%
      rename(
            D = `b[(Intercept) Leafhabit:D]`,
            E = `b[(Intercept) Leafhabit:E]`,
            S = `b[(Intercept) Leafhabit:SD]`) %>%
      mutate(E_S = E -  S) %>%
      mutate(S_D = S -  D) %>%
      mutate(E_D = E -  D)
  lwr <- 1 - 0.05/6
  upr <- 0 + 0.05/6

  lwr2 <- p_mat %>%
    dplyr::select(6:8) %>%
    apply(., 2, function(x)quantile(x, lwr))
  upr2 <- p_mat %>%
    dplyr::select(6:8) %>%
    apply(., 2, function(x)quantile(x, upr))
  # +1 indicautes signficance
   signs <- sign(lwr2 * upr2)
   signs[signs == 1] <- 0.01
   signs[signs == -1] <- 0.8

  means <- p_mat %>%
    rename(SD = S) %>%
    dplyr::select(E, SD, D) %>%
    apply(., 2, mean) %>% as.numeric

  alpha <- 0.05

  pvalue<-matrix(1,nrow=3,ncol=3)
  pvalue[1,2]<-pvalue[2,1]<-signs[1]
  pvalue[2,3]<-pvalue[3,2]<-signs[2]
  pvalue[1,3]<-pvalue[3,1]<-signs[3]

  treatments <- c("E", "SD", "D")

  out <- agricolae::orderPvalue(treatments, means, alpha, pvalue, console=TRUE)
  out$LH <- rownames(out) %>% factor(., levels = treatments)
  out2 <- out[order(out$LH), 2]
  c("E_letter" = out2[1], "SD_letter" = out2[2], "D_letter" = out2[3])
}

letter_fun2 <- function(fit) {
  p_mat <- as_tibble(fit) %>%
      rename(
            L = `b[(Intercept) Lifeform:L]`,
            S = `b[(Intercept) Lifeform:S]`,
            T = `b[(Intercept) Lifeform:T]`) %>%
      mutate(T_S = T -  S) %>%
      mutate(S_L = S -  L) %>%
      mutate(T_L = T -  L)
  lwr <- 1 - 0.05/6
  upr <- 0 + 0.05/6

  lwr2 <- p_mat %>%
    dplyr::select(6:8) %>%
    apply(., 2, function(x)quantile(x, lwr))
  upr2 <- p_mat %>%
    dplyr::select(6:8) %>%
    apply(., 2, function(x)quantile(x, upr))
  # +1 indicautes signficance
   signs <- sign(lwr2 * upr2)
   signs[signs == 1] <- 0.01
   signs[signs == -1] <- 0.8

  means <- p_mat %>%
    dplyr::select(L, S, T) %>%
    apply(., 2, mean) %>% as.numeric %>%
    round(2)

  alpha <- 0.05

  pvalue<-matrix(1,nrow=3,ncol=3)
  pvalue[1,2]<-pvalue[2,1]<-signs[1]
  pvalue[2,3]<-pvalue[3,2]<-signs[2]
  pvalue[1,3]<-pvalue[3,1]<-signs[3]
#  colnames(pvalue) <- rownames(pvalue) <- names(signs)

  treatments <- c("T", "S", "L")

  out <- agricolae::orderPvalue(treatments, means, alpha, pvalue, console=TRUE)
  out$LH <- rownames(out) %>% factor(., levels = treatments)
  out2 <- out[order(out$LH), 2]
  c("T_letter" = out2[1], "S_letter" = out2[2], "L_letter" = out2[3])
}

upr_fun <- function(fit) {
  p_mat <- as_tibble(fit) %>%
      rename(
            D_upr = `b[(Intercept) Leafhabit:D]`,
            E_upr = `b[(Intercept) Leafhabit:E]`,
            SD_upr = `b[(Intercept) Leafhabit:SD]`)  %>%
  dplyr::select(E_upr, SD_upr, D_upr)
  means <- p_mat %>%
    apply(., 2, function(x)quantile(x, 0.975))
  means %>% round(2)
}


lwr_fun <- function(fit) {
  p_mat <- as_tibble(fit) %>%
      rename(
            D_lwr = `b[(Intercept) Leafhabit:D]`,
            E_lwr = `b[(Intercept) Leafhabit:E]`,
            SD_lwr = `b[(Intercept) Leafhabit:SD]`)  %>%
  dplyr::select(E_lwr, SD_lwr, D_lwr)
  means <- p_mat %>%
    apply(., 2, function(x)quantile(x, 0.025))
  means %>% round(2)
}


upr_fun2 <- function(fit) {
  p_mat <- as_tibble(fit) %>%
      rename(
            L_upr = `b[(Intercept) Lifeform:L]`,
            S_upr = `b[(Intercept) Lifeform:S]`,
            T_upr = `b[(Intercept) Lifeform:T]`)  %>%
  dplyr::select(L_upr, S_upr, T_upr)
  means <- p_mat %>%
    apply(., 2, function(x)quantile(x, 0.975))
  means %>% round(2)
}

lwr_fun2 <- function(fit) {
  p_mat <- as_tibble(fit) %>%
      rename(
            L_lwr = `b[(Intercept) Lifeform:L]`,
            S_lwr = `b[(Intercept) Lifeform:S]`,
            T_lwr = `b[(Intercept) Lifeform:T]`)  %>%
  dplyr::select(L_lwr, S_lwr, T_lwr)
  means <- p_mat %>%
    apply(., 2, function(x)quantile(x, 0.025))
  means %>% round(2)
}

```


We applied the above functions and get the results.

```{r}
tmp <- nd_anova %>%
  mutate(map_dfr(trait_LH, mean_fun)) %>%
  mutate(map_dfr(trait_LH, upr_fun)) %>%
  mutate(map_dfr(trait_LH, lwr_fun)) %>%
  mutate(map_dfr(trait_LH, sig_fun)) %>%
  mutate(orderP = map(trait_LH, letter_fun)) %>%
  mutate(E_letter = map_chr(orderP,  ~ .[1])) %>%
  mutate(SD_letter = map_chr(orderP,  ~ .[2])) %>%
  mutate(D_letter = map_chr(orderP,  ~ .[3])) %>%
  mutate(map_dfr(trait_LF, mean_fun2)) %>%
  mutate(map_dfr(trait_LF, upr_fun2)) %>%
  mutate(map_dfr(trait_LF, lwr_fun2)) %>%
  mutate(map_dfr(trait_LF, sig_fun2)) %>%
  mutate(orderP2 = map(trait_LF, letter_fun2)) %>%
  mutate(T_letter = map_chr(orderP2,  ~ .[1])) %>%
  mutate(S_letter = map_chr(orderP2,  ~ .[2])) %>%
  mutate(L_letter = map_chr(orderP2,  ~ .[3])) %>%
  dplyr::select(-2:-5) %>%
  dplyr::select(-orderP, -orderP2) %>%
  ungroup

tmp[str_detect(tmp$name, "log10"), 2:10] <- round(10^tmp[str_detect(tmp$name, "log10"), 2:10], 2)
tmp[str_detect(tmp$name, "log10"), 17:25] <- round(10^tmp[str_detect(tmp$name, "log10"), 17:25], 2)

letter_dat <- tmp %>%
  mutate(name2 = factor(name,
                       levels = c(
                                  "log10KS",
                                  "P50",
                                  "P88",
                                  "MVL",
                                  "HV",
                                  "Fmin",
                                  "rxyl",
                                  "log10WOODSWC",
                                  "po",
                                  "ptlp",
                                  "log10SWCleaf",
                                  "log10Cft",
                                  "log10epsilon",
                                  "RWCtlp",
                                  "log10LMA",
                                  "log10rleaf",
                                  "HSM50",
                                  "HSM88",
                                  "HSMTLP"
                       ))) %>%
  mutate(name3 = case_when(
  name == "log10KS" ~ "$\\mathrm{K_s}$",
  name == "log10Cft" ~ "$\\mathrm{C_{leaf}}$",
  name == "P50" ~ "$\\mathrm{P_{50}}$",
  name == "P88" ~ "$\\mathrm{P_{88}}$",
  name == "HSM50" ~ "$\\mathrm{HSM_{50}}$",
  name == "HSM88" ~ "$\\mathrm{HSM_{88}}$",
  name == "HSMTLP" ~ "$\\mathrm{HSM_{tlp}}$",
  name == "po" ~ "$\\mathrm{\\pi_o}$",
  name == "ptlp" ~ "$\\mathrm{\\pi_{tlp}}$",
  name == "HV" ~ "$\\mathrm{H_V}$",
  name == "Fmin" ~ "$\\mathrm{\\Psi_{min}}$",
  name == "log10epsilon" ~ "$\\mathrm{\\epsilon}$",
  name == "log10LMA" ~ "LMA",
  name == "MVL" ~ "MVL",
  name == "log10SWCleaf" ~ "$\\mathrm{SWC_{leaf}}$",
  name == "log10WOODSWC" ~ "$\\mathrm{SWC_{wood}}$",
  name == "RWCtlp" ~ "$\\mathrm{RWC_{tlp}}$",
  name == "log10rleaf" ~ "$\\mathrm{\\rho_{leaf}}$",
  name == "rxyl" ~ "$\\mathrm{\\rho_{wood}}$",
  name == "diback" ~ "Branch die-back (%)",
  name == "mort" ~ "Whole-plant mortality (%)",
  TRUE ~ name,)) %>%
  mutate(tmp1 = paste(E_letter, SD_letter, D_letter, sep ="_")) %>%
  mutate(tmp2 = paste(T_letter, S_letter, L_letter, sep ="_")) %>%
  mutate(letter_LH =
  case_when(
            tmp1 == "b_ab_a" ~ "a_ab_b",
            tmp1 == "b_b_a" ~ "a_a_b",
            tmp1 == "c_b_a" ~ "a_b_c",
  TRUE ~ tmp1)) %>%
  mutate(letter_LF =
  case_when(
            tmp2 == "b_a_b" ~ "a_b_c",
            tmp2 == "b_ab_a" ~ "a_ab_b",
            tmp2 == "b_b_a" ~ "a_a_b",
            tmp2 == "c_b_a" ~ "a_b_c",
  TRUE ~ tmp2))  %>%
  mutate(S_letter2 = str_split_fixed(letter_LF, "_", 3)[,1]) %>%
  mutate(T_letter2 = str_split_fixed(letter_LF, "_", 3)[,2]) %>%
  mutate(L_letter2 = str_split_fixed(letter_LF, "_", 3)[,3]) %>%
  mutate(E_letter2 = str_split_fixed(letter_LH, "_", 3)[,1]) %>%
  mutate(SD_letter2 = str_split_fixed(letter_LH, "_", 3)[,2]) %>%
  mutate(D_letter2 = str_split_fixed(letter_LH, "_", 3)[,3]) %>%
  mutate(S = paste0(S, " [", S_lwr, ", ", S_upr, "]^", S_letter2, "^")) %>%
  mutate(T = paste0(T, " [", T_lwr, ", ", T_upr, "]^", T_letter2, "^")) %>%
  mutate(L = paste0(L, " [", L_lwr, ", ", L_upr, "]^", L_letter2, "^")) %>%
  mutate(E = paste0(E, " [", E_lwr, ", ", E_upr, "]^", E_letter2, "^")) %>%
  mutate(SD = paste0(SD, " [", SD_lwr, ", ", SD_upr, "]^", SD_letter2, "^")) %>%
  mutate(D = paste0(D, " [", D_lwr, ", ", D_upr, "]^", D_letter2, "^")) %>%
  dplyr::select(name2,name3,
                E, SD, D, E_letter, SD_letter, D_letter, tmp1, letter_LH,
      S, T, L, T_letter, S_letter, L_letter, tmp2, letter_LF
  )

letter_dat %>%
  arrange(name2) %>%
  kable()  %>%
  kable_styling()

```

# Model for branch die-back and top-kill ratios

Next, we model branch die-back and top-kill ratio using logistic functions.

```{r,eval=TRUE}

model_B_LH <- stan_glmer(cbind(DeadBranch, AllBranch - DeadBranch) ~ 0 +  (1|Leafhabit),
                                    iter = n_iter,
                                    chains = n_chain,
                                    refresh = 0,
                                    prior = my_prior,
                                    prior_aux = my_prior_aux,
                                    prior_intercept = my_prior,
                                    adapt_delta = 0.99,
                                    data = d, family = binomial)

model_B_LF <- stan_glmer(cbind(DeadBranch, AllBranch - DeadBranch) ~ 0 +
                         (1|Lifeform),
                                    iter = n_iter,
                                    chains = n_chain,
                                    refresh = 0,
                                    prior = my_prior,
                                    prior_aux = my_prior_aux,
                                    prior_intercept = my_prior,
                                    adapt_delta = 0.99,
                                    data = d, family = binomial)

model_T_LH <- stan_glmer(cbind(DeadTree, AllTree - DeadTree) ~ 0 +  (1|Leafhabit),
                                    iter = n_iter,
                                    chains = n_chain,
                                    refresh = 0,
                                    prior = my_prior,
                                    prior_aux = my_prior_aux,
                                    prior_intercept = my_prior,
                                    adapt_delta = 0.99,
                                    data = d, family = binomial)
model_T_LF <- stan_glmer(cbind(DeadTree, AllTree - DeadTree) ~ 0 +
                         (1|Lifeform),
                                    iter = n_iter,
                                    chains = n_chain,
                                    refresh = 0,
                                    prior = my_prior,
                                    prior_aux = my_prior_aux,
                                    prior_intercept = my_prior,
                                    adapt_delta = 0.99,
                                    data = d, family = binomial)
```


Here are utility functions to extract the results.

```{r}
letter_fun3 <- function(fit) {
  p_mat <- as_tibble(fit) %>%
      rename(
            D = `b[(Intercept) Leafhabit:D]`,
            E = `b[(Intercept) Leafhabit:E]`,
            S = `b[(Intercept) Leafhabit:SD]`) %>%
      mutate(E_S = E -  S) %>%
      mutate(S_D = S -  D) %>%
      mutate(E_D = E -  D)
  lwr <- 0 + 0.05/6
  upr <- 1 - 0.05/6
#  lwr <- 0.025
#  upr <- 0.975
  lwr2 <- p_mat %>%
    dplyr::select(5:7) %>%
    apply(., 2, function(x)quantile(x, lwr))
  upr2 <- p_mat %>%
    dplyr::select(5:7) %>%
    apply(., 2, function(x)quantile(x, upr))
  # +1 indicautes signficance
   signs <- sign(lwr2 * upr2)
   signs[signs == 1] <- 0.01
   signs[signs == -1] <- 0.8

  means <- p_mat %>%
    rename(SD = S) %>%
    dplyr::select(E, SD, D) %>%
    apply(., 2, mean) %>% as.numeric

  alpha <- 0.05

  pvalue<-matrix(1,nrow=3,ncol=3)
  pvalue[1,2]<-pvalue[2,1]<-signs[1]
  pvalue[2,3]<-pvalue[3,2]<-signs[2]
  pvalue[1,3]<-pvalue[3,1]<-signs[3]
#  colnames(pvalue) <- rownames(pvalue) <- names(signs)

  treatments <- c("E", "SD", "D")

  out <- agricolae::orderPvalue(treatments, means, alpha, pvalue, console=TRUE)
  out$LH <- rownames(out) %>% factor(., levels = treatments)
  out2 <- out[order(out$LH), 2]
  c("E_letter" = out2[1], "SD_letter" = out2[2], "D_letter" = out2[3])
}

letter_fun4 <- function(fit) {
  fit <- model_T_LF
  p_mat <- as_tibble(fit) %>%
      rename(
            L = `b[(Intercept) Lifeform:L]`,
            S = `b[(Intercept) Lifeform:S]`,
            T = `b[(Intercept) Lifeform:T]`) %>%
      mutate(T_S = T -  S) %>%
      mutate(S_L = S -  L) %>%
      mutate(T_L = T -  L)
  lwr <- 0 + 0.05/6
  upr <- 1 - 0.05/6
  lwr2 <- p_mat %>%
    dplyr::select(5:7) %>%
    apply(., 2, function(x)quantile(x, lwr))
  upr2 <- p_mat %>%
    dplyr::select(5:7) %>%
    apply(., 2, function(x)quantile(x, upr))
  # +1 indicautes signficance
   signs <- sign(lwr2 * upr2)
   signs[signs == 1] <- 0.01
   signs[signs == -1] <- 0.8

  means <- p_mat %>%
    dplyr::select(L, S, T) %>%
    apply(., 2, mean) %>% as.numeric %>%
    round(2)

  alpha <- 0.05

  pvalue<-matrix(1,nrow=3,ncol=3)
  pvalue[1,2]<-pvalue[2,1]<-signs[1]
  pvalue[2,3]<-pvalue[3,2]<-signs[2]
  pvalue[1,3]<-pvalue[3,1]<-signs[3]

  treatments <- c("T", "S", "L")

  out <- agricolae::orderPvalue(treatments, means, alpha, pvalue, console=TRUE)
  out$LH <- rownames(out) %>% factor(., levels = treatments)
  out2 <- out[order(out$LH), 2]
  c("T_letter" = out2[1], "S_letter" = out2[2], "L_letter" = out2[3])
}

```

We get letters that describe significance.

```{r}
tmp1 <- letter_fun3(model_B_LH) %>%
  paste(collapse = "_")
tmp2 <- letter_fun3(model_T_LH) %>%
  paste(collapse = "_")
tmp1
tmp2
letter_LH <- c(tmp1, tmp2)

tmp3 <- letter_fun4(model_B_LF) %>%
  paste(collapse = "_")
tmp4 <- letter_fun4(model_T_LF) %>%
  paste(collapse = "_")
tmp3
tmp4
letter_LF <- c(tmp3, tmp4)

```

We get the posterior distributions of branch dieback and top-kill ratios for
the each leaf habit and growth form.

```{r}
my_logistic <- function(x)
  {
     (1 / (1 + exp(-x)) * 100) %>% round(2)
  }

binom_fun <- function(fit, LH = TRUE) {
  if (LH) {
    p_mat <- as_tibble(fit) %>%
        rename(
              D_upr = `b[(Intercept) Leafhabit:D]`,
              E_upr = `b[(Intercept) Leafhabit:E]`,
              SD_upr = `b[(Intercept) Leafhabit:SD]`)  %>%
    dplyr::select(E_upr, SD_upr, D_upr)
  } else {
    p_mat <- as_tibble(fit) %>%
        rename(
              L_lwr = `b[(Intercept) Lifeform:L]`,
              S_lwr = `b[(Intercept) Lifeform:S]`,
              T_lwr = `b[(Intercept) Lifeform:T]`)  %>%
    dplyr::select(T_lwr, S_lwr, L_lwr)
  }

  means <- p_mat %>%
    apply(., 2, mean) %>%
    my_logistic
  lwr <- p_mat %>%
    apply(., 2, function(x)quantile(x, 0.025)) %>%
    my_logistic
  upr <- p_mat %>%
    apply(., 2, function(x)quantile(x, 0.975)) %>%
    my_logistic
  paste0(means, " [", lwr, ", ", upr, "]")
}


lh1 <- rbind(
          binom_fun(model_B_LH, LH = TRUE),
          binom_fun(model_T_LH, LH = TRUE))
colnames(lh1) <- c("E", "SD", "D")
lh2 <- lh1 %>%
  as_tibble %>%
  mutate(name2 = c("Branch dieback ratio (%)", "Top-kill ratio (%)"))
lf1 <- rbind(binom_fun(model_B_LF, LH = FALSE),
        binom_fun(model_T_LF, LH = FALSE))
colnames(lf1) <- c("S", "T", "L")
lf2 <- lf1 %>%
  as_tibble

letter_dat2 <- bind_cols(lh2, lf2) %>%
  mutate(letter_LF, letter_LH) %>%
  mutate(letter_LH2 =
  case_when(
            letter_LH == "b_a_b" ~ "a_b_a",
            TRUE ~ "hoge")) %>%
  mutate(letter_LF2 =
  case_when(
            letter_LF == "b_a_b" ~ "a_b_a",
            letter_LF == "b_a_ab" ~ "a_b_ab",
            TRUE ~ "hoge"))
letter_dat2 %>%
  kable() %>%
  kable_styling()
```


# Table

```{r}
tb_dat <- letter_dat %>%
  dplyr::select(name2, E, SD, D, S, T, L) %>%
  bind_rows(
   letter_dat2 %>%
   dplyr::select(name2, E, SD, D, S, T, L)) %>%
  mutate(name_fct = factor(name2,
                       levels = c(
                                  "log10KS",
                                  "P50",
                                  "P88",
                                  "MVL",
                                  "HV",
                                  "Fmin",
                                  "rxyl",
                                  "log10WOODSWC",
                                  "po",
                                  "ptlp",
                                  "log10SWCleaf",
                                  "log10Cft",
                                  "log10epsilon",
                                  "RWCtlp",
                                  "log10LMA",
                                  "log10rleaf",
                                  "HSM50",
                                  "HSM88",
                                  "HSMTLP",
        "Branch dieback ratio (%)", "Top-kill ratio (%)"
                       ))) %>%
  mutate(name_greek = case_when(
  name2 == "log10KS" ~ "$\\mathrm{K_s\\;(kg\\; m^{-1} \\; s^{-1}\\; MPa^{-1})}$",
  name2 == "log10Cft" ~ "$\\mathrm{C_{leaf}}$ (mol m^-2^ MPa^-1^)",
  name2 == "P50" ~ "$\\mathrm{P_{50}}$ (MPa)",
  name2 == "P88" ~ "$\\mathrm{P_{88}}$ (MPa)",
  name2 == "HSM50" ~ "$\\mathrm{HSM_{50}}$ (MPa)",
  name2 == "HSM88" ~ "$\\mathrm{HSM_{88}}$ (MPa)",
  name2 == "HSMTLP" ~ "$\\mathrm{HSM_{tlp}}$ (MPa)",
  name2 == "po" ~ "$\\mathrm{\\pi_o}$ (MPa)",
  name2 == "ptlp" ~ "$\\mathrm{\\pi_{tlp}}$ (MPa)",
  name2 == "HV" ~ "$\\mathrm{H_V}$ (mm^2^ cm^-2^)",
  name2 == "Fmin" ~ "$\\mathrm{\\Psi_{min}}$ (MPa)",
  name2 == "log10epsilon" ~ "$\\mathrm{\\epsilon}$ (MPa)",
  name2 == "log10LMA" ~ "LMA (g cm^-2^)",
  name2 == "MVL" ~ "MVL (cm)",
  name2 == "log10SWCleaf" ~ "$\\mathrm{SWC_{leaf}}$ (g g^-1^)",
  name2 == "log10WOODSWC" ~ "$\\mathrm{SWC_{wood}}$ (g g^-1^)",
  name2 == "RWCtlp" ~ "$\\mathrm{RWC_{tlp}}$ (MPa)",
  name2 == "log10rleaf" ~ "$\\mathrm{\\rho_{leaf}}$ (g cm^-3^)",
  name2 == "rxyl" ~ "$\\mathrm{\\rho_{wood}}$ (g cm^-3^)",
  name2 == "diback" ~ "Branch die-back (%)",
  name2 == "mort" ~ "Whole-plant mortality (%)",
  TRUE ~ name2,)) %>%
  arrange(name_fct)

tb_dat %>%
  dplyr::select(Traits = name_greek,
                `Evergreen n = 9` = E,
                `Semi-deciduous n = 16` = SD,
                `Deciduous n = 15` = D,
                `Tree n = 17` = T,
                `Shrub n = 16` = S,
                `Liana n = 7` = L
  ) %>%
  kable()  %>%
  pack_rows("Stem traits", 1, 8) %>%
  pack_rows("Leaf traits", 9, 16) %>%
  pack_rows("Safety margins", 17, 19) %>%
  pack_rows("Whole-plant performance", 20, 21) %>%
  kable_styling() %>%
  add_header_above(c(" " = 1, "Leaf habit" = 3, "Growth form" = 3))
```

**Table 1.** Comparison on leaf and stem traits, hydraulic safety margins, branch dieback and top-kill ratios among three leaf habit types and three growth forms for 40 species from a hot-dry savanna of southwest China.
Values and values in brackets are the posterior mean and the 95% credible interval, respectively.
Effects sharing the same letters are not significantly different at the $\alpha$ = 0.05 level (98.3% CI).

# Computing Environment

```{r}
devtools::session_info()
```

